Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2020-04-06 paper/notes.tex
More notation tweaks

the term for the divergence of $\mb{J}$ can be written:
%
\begin{equation}
  \label{eq:divJ}
  \nabla\vcdot\mb{J}_i(\mb{x},t) = \nabla\vcdot\left(D \nabla a_i-a_i\sum_{j=1}^{M} \gamma_{i,j}\nabla \rho_j(\mb{x})\right).
\end{equation}
%
In the barrels model, each $\rho_j(\mb{x})$ was assumed static, allowing the
definition of a time-independent $\mb{g}_i(\mb{x})$:
%
\begin{equation}
\mb{g}_i(\mb{x}) \equiv \sum_{j=1}^{M} \gamma_{i,j} \nabla\rho_j(\mb{x}).
\end{equation}
%
Here, we represent the time-dependence of the signalling molecule expression
by noting that $\rho$ is now a function of time.  The error which the growth
cones make in sampling $\rho$ and estimating $\nabla\rho_j(\mb{x})$ is
$\xi_{\rho'}(t)$:
%
\begin{equation}
\mb{g}_i(\mb{x},t) \equiv \sum_{j=1}^{M} \gamma_{i,j} \big( \nabla\rho_j(\mb{x},t)
+ \xi_{\rho'}(t) \big).
\end{equation}
%
One problem with this representation is that the equations represent a
population model. Within one spatial element of the discretized solution of
the differential equations, the error, $\xi_\rho(t)$ can have only one value at
time $t$; this value is applied to all the individual axon growth cones that
are represented by that element. Nonetheless, it's a useful, and fairly simple
way to represent the guidance error in the system. In practice, we ignore the
variation in $\rho_j$ and write
%
\begin{equation}
\mb{g}_i(\mb{x},t) \equiv \sum_{j=1}^{M} \gamma_{i,j} \big( \nabla\rho_j(\mb{x})
+ \xi_{\rho'}(t) \big).
\end{equation}

$\xi_\rho(t)$ will be included in the model as a function returning numbers sampled
from a normal distribution with mean 0 and standard deviation $\sigma_\rho$.

@@

$\xi_\gamma$ is drawn from a normal distribution with mean 0 and standard
deviation $\sigma_\rho$.

@@

\begin{equation} \label{eq:da_stopping}
\frac{\partial a_i}{\partial t} = \nabla\vcdot\left(D \nabla a_i-a_i\sum_{j=1}^{M=2} \gamma_{i,j}\nabla \rho_j(\mb{x})\right)\;f\big(\gamma_{i,1},\gamma_{i,2},\tilde{\rho}_{1}(\mb{x}),\tilde{\rho}_{2}(\mb{x})\big) - \frac{\partial c_i}{\partial t},
\end{equation}

Where $f$ is a function which permits branching far away from a given axon's
target region and tends to zero inside the target region. It represents an
axon's internal `stopping process'. Note that $\tilde{\rho}_j(\mb{x})$ is the
axon's measurement of $\rho_j(\mb{x})$ and may include measurement noise,
$\xi_\rho$: $\tilde{\rho}_j = \rho_j + \xi_\rho$. Given that the morphogen
gradients are orthogonal, $(\tilde{\rho}_1,\tilde{\rho}_2)$ defines a vector
field $\vec{\rho}(\mb{x})$. Similarly, we can combine
$(\gamma_{i,1},\gamma_{i,2})$ into the vector $\vec{\gamma}$.

This makes it easy to start to build $f$ with a two dimensional Gaussian
function:

\begin{equation}\label{eq:g}
g\big(\vec{\rho}(\mb{x})\big) = \mathrm{e}^{-\big(\frac{\vec{\rho}(\mb{x})-\vec{\gamma}}{2 w}\big)^2 }
\end{equation}

where $\vec{\gamma}$ gives the location of the peak and $w$ is the width
of the peak. This is squashed through an inverting sigmoid, with sharpness $s$:

\begin{equation}\label{eq:f}
f\big(\vec{\rho}(\mb{x})\big) = \frac{2}{1 + \mathrm{e}^{-s g(\vec{\rho}\,)}} - 1
\end{equation}

@@

\begin{equation}\label{eq:gf}
f(\vec{\rho}(\mb{x})) = \frac{2}{1
+ \mathrm{e}^{-s \mathrm{e}^{-\big(\frac{\vec{\rho}(\mb{x})-\vec{\gamma}}{2 w}\big)^2 } }} - 1
\end{equation}

>>>>

the term for the divergence of $\mb{J}$ can be written:
%
\begin{equation}
  \label{eq:divJ}
  \nabla\vcdot\mb{J}_i(\mb{x},t) = \nabla\vcdot\left(D \nabla a_i-a_i\sum_{j=1}^{M} \gamma_{i,j}\nabla \rho_j(\mb{x})\right).
\end{equation}
%
In the barrels model, each $\rho_j(\mb{x})$ was assumed static, allowing the
definition of a time-independent $\mb{g}_i(\mb{x})$:
%
\begin{equation}
\mb{g}_i(\mb{x}) \equiv \sum_{j=1}^{M} \gamma_{i,j} \nabla\rho_j(\mb{x}).
\end{equation}
%
Here, we represent the time-dependence of the signalling molecule expression
by noting that $\rho$ is now a function of time.  The error which the growth
cones make in sampling $\rho$ and estimating $\nabla\rho_j(\mb{x})$ is
$\xi_{\rho'}(t)$:
%
\begin{equation}
\mb{g}_i(\mb{x},t) \equiv \sum_{j=1}^{M} \gamma_{i,j} \big( \nabla\rho_j(\mb{x},t)
+ \xi_{\rho'}(t) \big).
\end{equation}
%
One problem with this representation is that the equations represent a
population model. Within one spatial element of the discretized solution of
the differential equations, the error, $\xi_{\rho'}(t)$ can have only one value at
time $t$; this value is applied to all the individual axon growth cones that
are represented by that element. Nonetheless, it's a useful, and fairly simple
way to represent the guidance error in the system. In practice, we ignore the
variation in $\rho_j$ and write
%
\begin{equation}
\mb{g}_i(\mb{x},t) \equiv \sum_{j=1}^{M} \gamma_{i,j} \big( \nabla\rho_j(\mb{x})
+ \xi_{\rho'}(t) \big).
\end{equation}

$\xi_{\rho'}(t)$ will be included in the model as a function returning numbers sampled
from a normal distribution with mean 0 and standard deviation $\sigma_{\rho'}$.

@@

$\xi_\gamma$ is drawn from a normal distribution with mean 0 and standard
deviation $\sigma_{\gamma}$.

@@

\begin{equation} \label{eq:da_stopping}
\frac{\partial a_i}{\partial t} = \nabla\vcdot\left(D \nabla a_i-a_i\sum_{j=1}^{M=2} \gamma_{i,j}\nabla \rho_j(\mb{x})\right)\;f_i\big(\gamma_{i,1},\gamma_{i,2},\tilde{\rho}_{1}(\mb{x}),\tilde{\rho}_{2}(\mb{x})\big) - \frac{\partial c_i}{\partial t},
\end{equation}

Where $f_i$ is a function which permits branching far away from a given axon's
target region and tends to zero inside the target region. It represents an
axon's internal `stopping process'. Note that $\tilde{\rho}_j(\mb{x})$ is the
axon's measurement of $\rho_j(\mb{x})$ and may include measurement noise,
$\xi_\rho$: $\tilde{\rho}_j = \rho_j + \xi_\rho$. Given that the morphogen
gradients are orthogonal, $(\tilde{\rho}_1,\tilde{\rho}_2)$ defines a vector
field $\vec{\rho}(\mb{x})$. Similarly, we can combine
$(\gamma_{i,1},\gamma_{i,2})$ into the vector $\vec{\gamma}$.

This makes it easy to start to build $f_i$ with a two dimensional Gaussian
function:

\begin{equation}\label{eq:g}
g_i\big(\vec{\rho}(\mb{x})\big) = \mathrm{e}^{-\big(\frac{\vec{\rho}(\mb{x})-\vec{\gamma}}{2 w}\big)^2 }
\end{equation}

where $\vec{\gamma}$ gives the location of the peak and the parameter $w$ is
the width of the peak. This is squashed through an inverting sigmoid, with
sharpness parameter $s$:

\begin{equation}\label{eq:f}
f_i\big(\vec{\rho}(\mb{x})\big) = \frac{2}{1 + \mathrm{e}^{-s g_i(\vec{\rho}\,)}} - 1
\end{equation}

@@

\begin{equation}\label{eq:gf}
f_i\big(\vec{\rho}(\mb{x})\big) = \frac{2}{1
+ \mathrm{e}^{-s \mathrm{e}^{-\big(\frac{\vec{\rho}(\mb{x})-\vec{\gamma}}{2 w}\big)^2 } }} - 1
\end{equation}
